A Blockchain Consensus Protocol with\\Horizontal Scalability

### 2018-05-15 conference-presentation/presentation.tex
Add conference location

@@

\title{A Blockchain Consensus Protocol With\\Horizontal Scalability}
% \subtitle{Optional Subtitle}

@@

\author[Short Name (U ABC)]{%
  \texorpdfstring{%
    \begin{columns}
      \column{.3333\linewidth}
      \centering
      Kelong~Cong \\ \small kelong.cong@epfl.ch \\ EPFL
      \column{.3333\linewidth}
      \centering
      Zhijie~Ren \\ \small z.ren@tudelft.nl \\ TU Delft
      \column{.3333\linewidth}
      \centering
      Johan~Pouwelse \\ \small peer2peer@gmail.com \\ TU Delft
    \end{columns}
 }
 {Author 1, Author 2, Author 3}
}

% \date{Conference Name, 2013}
\date{IFIP Networking, 2018}

@@

\begin{frame}{Blockchain:~not there yet}
  \begin{itemize}
    \item All blockchain systems have a consensus algorithm
    \item Early consensus algorithms (PoW) do not scale
    \item Bitcoin is limited to 7 transactions per second
    \item 100,000 transaction backlog in May 2017
    \item We require horizontal scalability for ubiquitous use
    \item More users $\rightarrow$ more transactions per second globally
  \end{itemize}
\end{frame}

\subsection{Related work}
\begin{frame}{Related work}
    \begin{itemize}
        \item Off-chain solution
            \begin{itemize}
                \item Lightning Network\footnote{\url{https://lightning.network/}}
                \item Perun\footnote{\url{https://perun.network}}
            \end{itemize}
        \item On-chain solution
            \begin{itemize}
                \item Parameter tuning
                \item BFT consensus (e.g. Tendermint\footnote{\url{https://www.tendermint.com/}}, ByzCoin\footnote{KJGKGF, USENIXSecurity16})
                \item Sharding (e.g. Elastico\footnote{LNZBGS, CCS16}, OmniLedger\footnote{KJGGSF, S\&P18})
            \end{itemize}
    \end{itemize}
\end{frame}

@@

\subsection{Research question}
\begin{frame}{\subsecname}
  \begin{block}{}
    \Large{
    How can we design a \emph{blockchain consensus protocol} that is \emph{fault-tolerant},
    \emph{horizontally scalable}, and able to reach \emph{global consensus?}
    }
  \end{block}
  \begin{itemize}
    \item Blockchain consensus protocol---application neutral, e.g., PoW
    \item Fault-tolerant---tolerate a number of malicious nodes
    \item Horizontal scalability---more nodes in the network leads to higher transaction throughput
    \item Global consensus---all node should agree on a global state
  \end{itemize}
\end{frame}

@@

\subsection{System model}
\subsection{Architecture overview}
\begin{frame}{\subsecname}
  \begin{center}
  {\Large The four components of \textsc{Checo}}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{architecture-wo-title}
  \centering
  \end{figure}
  \end{center}
  \note{
    \begin{itemize}
    \item The primary data structure is the Extended TrustChain, extension of our prior work
    \item The three protocols the tasks as their name suggests
    \item They are independent and run concurrently
    \item The only synchronisation happens via the Extended TrustChain
    \item But in no part of those protocol do we lock the Extended TrustChain
    \end{itemize}
  }
\end{frame}

\subsection{Extended TrustChain}
\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.75\textwidth]{trustchain-good-cp}
  \centering
  \end{figure}
  \note{
    \begin{itemize}
      \item In this example there are three nodes
      \item Each node maintains their personal hash chain and genesis block
      \item Squares are TX blocks and circles are CP blocks
      \item Explain the block content in caption
      \item The dotted line represent pairs of TX blocks
      \item Geared with the understanding of our data structure, we are ready to talk about the consensus protocol
    \end{itemize}
  }
\end{frame}

\begin{frame}{\subsecname:~Transaction (TX) block}
\begin{itemize}
  \item Goal: record transactions
  \item A transaction is represented by a pair of TX blocks,
  i.e. a contract signed by both parties
\end{itemize}
\begin{figure}[h]
  \includegraphics[trim={7cm 8.2cm 2cm 2.55cm},clip,width=0.7\textwidth]{trustchain-good-cp}
  \centering
\end{figure}
\end{frame}

@@

\begin{frame}{\subsecname:~Fragment of a TX block}
  \begin{figure}[h]
  \includegraphics[width=0.75\textwidth]{trustchain-good-cp-frag}
  \centering
  \end{figure}
\end{frame}

@@

\begin{frame}{\subsecname:~properties}
\label{def:consensus}
\begin{itemize}
    \item \emph{Agreement}:
        Every correct outputs the same set of facilitators.
    \item \emph{Validity}:
      The consensus result is valid such that a new set of facilitators can be computed from it.
    % \item \emph{Fairness}:
    %     Every node with a CP block in the consensus result should have an equal probability of becoming a facilitator.
    \item \emph{Termination}:
        Every correct node eventually outputs a set of facilitators.
\end{itemize}
\end{frame}

\subsection{Transaction protocol}
\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=1.0\textwidth]{tx-proto}
  \centering
  \end{figure}
\begin{itemize}
\item Two TX blocks are generated on the chains of Alice and Bob
\item No guarantee that nodes follow this protocol
\end{itemize}
\end{frame}

@@

\section{Experimental results}
\begin{frame}{Implementation and experiment setup}
  \begin{itemize}
    \item Free and open source implementation on Github:
      \url{https://github.com/kc1212/checo}
    \item SHA256 for hash functions and Ed25519 for digital signature
    \item Experiment on the DAS-5\footnote{\url{http://www.cs.vu.nl/das5/}}
    \item Up to 1200 nodes
  \end{itemize}
\end{frame}

\begin{frame}{Validated transaction throughput (random node)}
  \begin{figure}[h]
  \includegraphics[width=0.9\textwidth]{neighbour-random/throughput-vs-population}
  \centering
  \end{figure}
\end{frame}

\begin{frame}{Validated transaction throughput (fixed neighbour)}
  \begin{figure}[h]
  \includegraphics[width=0.9\textwidth]{neighbour-fixed/throughput-vs-population}
  \centering
  \end{figure}
\note{No need to request for fragment every time a TX needs to be validated. Upon receiving a fragment, validate as many TX as possible.}
\end{frame}

\section{Conclusion}
\begin{frame}{\secname}
  Our work answers the research question.
  \begin{block}{}
    How can we design a \emph{blockchain consensus protocol} that is \emph{fault-tolerant},
    \emph{horizontally-scalable}, and able to reach \emph{global consensus?}
  \end{block}
  \begin{itemize}
    \item Fault-tolerance is achieved using HoneyBadgerBFT
    \item Horizontal-scalability is achieved by separating consensus and validation, demonstrated experimentally
    \item Global-consensus on transactions is achieved via consensus on CP blocks
  \end{itemize}
\end{frame}

@@

\begin{frame}{Thank you}
  \begin{center}
  {\Large Any questions?}
  \end{center}
\end{frame}

@@

\begin{frame}[noframenumbering]{Future work}
\begin{itemize}
\item Implement and experiment with a concrete application
\item Analyse the system in the permissionless environment
\item Improve fault tolerance
\end{itemize}
\end{frame}

\begin{frame}{Stress test (fixed neighbour)}
  \begin{figure}[h]
  \includegraphics[width=0.9\textwidth]{throughput-vs-population-large}
  \centering
  \end{figure}
\end{frame}

>>>>

\beamertemplatenavigationsymbolsempty
\setbeamertemplate{footline}[frame number]

@@

\title{A Blockchain Consensus Protocol with\\Horizontal Scalability}
% \subtitle{Optional Subtitle}

@@

\author[Short Name (U ABC)]{%
  \texorpdfstring{%
    \begin{columns}
      \column{.3333\linewidth}
      \centering
      Kelong~Cong \\ \small kelong.cong@epfl.ch \\ EPFL
      \column{.3333\linewidth}
      \centering
      Zhijie~Ren \\ \small z.ren@tudelft.nl \\ TU Delft
      \column{.3333\linewidth}
      \centering
      Johan~Pouwelse \\ \small peer2peer@gmail.com \\ TU Delft
    \end{columns}
 }
 {Kelong~Cong, Zhijie~Ren, Johan~Pouwelse}
}

% \date{Conference Name, 2013}
\date{IFIP Networking, Zurich 2018}

@@

\begin{frame}{Blockchain:~not there yet}
  \begin{itemize}
    \item All blockchain systems have a consensus algorithm
    \item Early consensus algorithms do not scale
    \item Bitcoin is limited to 7 transactions per second
    \item 100,000 transaction backlog in May 2017
    \item We require horizontal scalability for ubiquitous use
    \item More users $\rightarrow$ more transactions per second globally
  \end{itemize}
\end{frame}

\subsection{Related work}
\begin{frame}{Related work}
    \begin{itemize}
        \item Off-chain solution
            \begin{itemize}
                \item Lightning Network\footnote{\url{https://lightning.network/}}
                \item Perun\footnote{\url{https://perun.network}}
                \item Easy to deploy but application specific
            \end{itemize}
        \item On-chain solution
            \begin{itemize}
                \item Parameter tuning
                \item BFT consensus (e.g. Tendermint\footnote{\url{https://www.tendermint.com/}}, ByzCoin\footnote{KJGKGF, USENIXSecurity16})
                \item Sharding (e.g. Elastico\footnote{LNZBGS, CCS16}, OmniLedger\footnote{KJGGSF, S\&P18})
            \end{itemize}
    \end{itemize}
\end{frame}

@@

\subsection{Research question}
\begin{frame}{\subsecname}
  \begin{block}{}
    \Large{
    How can we design a \emph{blockchain consensus protocol} that is \emph{fault-tolerant},
    \emph{horizontally scalable}, and able to reach \emph{global consensus?}
    }
  \end{block}
  \begin{itemize}
    \item Blockchain consensus protocol---application neutral
    \item Fault-tolerant---tolerate a number of malicious nodes
    \item Horizontal scalability---more nodes in the network leads to higher transaction throughput
    \item Global consensus---all node should agree on a global state
  \end{itemize}
\end{frame}

@@

\subsection{System model}
\subsection{Architecture overview}
\begin{frame}{\subsecname}
  \begin{center}
  {\Large The four components of \textsc{Checo}\footnote{\textsc{Che}ckpoint \textsc{co}nsensus}} 
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{architecture-wo-title}
  \centering
  \end{figure}
  \end{center}
  \note{
    \begin{itemize}
    \item The primary data structure is the Extended TrustChain, extension of our prior work
    \item The three protocols the tasks as their name suggests
    \item They are independent and run concurrently
    \item The only synchronisation happens via the Extended TrustChain
    \item But in no part of those protocol do we lock the Extended TrustChain
    \end{itemize}
  }
\end{frame}

\subsection{Extended TrustChain}
\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.84\textwidth]{trustchain-good-cp}
  \centering
  \end{figure}
  \note{
    \begin{itemize}
      \item In this example there are three nodes
      \item Each node maintains their personal hash chain and genesis block
      \item Squares are TX blocks and circles are CP blocks
      \item Explain the block content in caption
      \item The dotted line represent pairs of TX blocks
      \item Geared with the understanding of our data structure, we are ready to talk about the consensus protocol
    \end{itemize}
  }
\end{frame}

\begin{frame}{\subsecname:~Transaction (TX) block}
\begin{itemize}
  \item Goal: record transactions
  \item A transaction is an agreement on a piece of data, i.e. digitally signed by both parties
  \item It is represented by a pair of TX blocks
\end{itemize}
\begin{figure}[h]
  \includegraphics[trim={7cm 8.2cm 2cm 2.55cm},clip,width=0.7\textwidth]{trustchain-good-cp}
  \centering
\end{figure}
\end{frame}

@@

\begin{frame}{\subsecname:~Fragment of a TX block}
  \begin{figure}[h]
  \includegraphics[width=0.84\textwidth]{trustchain-good-cp-frag}
  \centering
  \end{figure}
\end{frame}

@@

\subsection{Transaction protocol}
\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=1.0\textwidth]{tx-proto}
  \centering
  \end{figure}
\begin{itemize}
\item Two TX blocks are generated on the chains of Alice and Bob
\item No guarantee that nodes follow this protocol
\item Contrary to early blockchain systems, we do not broadcast transactions
\end{itemize}
\end{frame}

@@

\section{Experimental results}
\begin{frame}{Implementation and experiment setup}
  \begin{itemize}
    \item Free and open source implementation on Github:
      \url{https://github.com/kc1212/checo}
    \item SHA256 for hash functions and Ed25519 for digital signature
    \item Experiment on the DAS-5\footnote{\url{http://www.cs.vu.nl/das5/}}
    \item Up to 1200 nodes
    \item A third of the facilitators are malicious
  \end{itemize}
\end{frame}

\begin{frame}{Validated transaction throughput (random node)}
  \begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{neighbour-random/throughput-vs-population}
  \centering
  \end{figure}
\end{frame}

\begin{frame}{Validated transaction throughput (fixed neighbour)}
  \begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{neighbour-fixed/throughput-vs-population}
  \centering
  \end{figure}
\note{No need to request for fragment every time a TX needs to be validated. Upon receiving a fragment, validate as many TX as possible.}
\end{frame}

\section{Conclusion}
\begin{frame}{\secname}
    Our contribution:
  \begin{itemize}
      \item We design a blockchain consensus protocol---\textsc{Checo} with horizontal scalability
      \item We formally analyse CHECO to ensure correctness
      \item Our experimental evaluation show strong evidence of our claim.
  \end{itemize}
      Future perspective:
  \begin{itemize}
      \item Improve fault-tolerance using ByzCoinX from OmniLedger
      \item Design and evaluate UTXO-style transactions (new paper to appear in Crypto Valley Conference)
      \item Assume a permissionless model
  \end{itemize}
\end{frame}

@@

@@

\begin{frame}[noframenumbering]{Stress test (fixed neighbour)}
  \begin{figure}[h]
  \includegraphics[width=0.9\textwidth]{throughput-vs-population-large}
  \centering
  \end{figure}
\end{frame}
